### 2014-02-21 paper/conclusion.tex
more text, hooray

>>>>

Ten movies streaming across that, that Internet, and what happens to your own personal Internet? I just the other day got… an Internet [that was] sent by my staff at 10 o'clock in the morning on Friday. I got it yesterday [Tuesday]. Why? Because it got tangled up with all these things going on the Internet commercially.
[…] They want to deliver vast amounts of information over the Internet. And again, the Internet is not something that you just dump something on. It's not a big truck. It's a series of tubes. And if you don't understand, those tubes can be filled and if they are filled, when you put your message in, it gets in line and it's going to be delayed by anyone that puts into that tube enormous amounts of material, enormous amounts of material.

### 2014-02-21 paper/exampleobjects.tex
more text, hooray

We created a touch-sensitive toy and an app that goes along with it, reminiscent of the boat application in \cite{Harrison-acoustic}.  This toy has an interior star

\subsection{Braille Learning Tool}

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This box has 6 individually-actuated semi-closed tubes capped with rubberlike material.  When air pressure is changed in these tubes, the caps inflate or deflate.  By actuating these tubes in particular sets, we can create braille letters.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:braille}
\end{figure}

@@

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This pen holder (a) uses Wimmer's FlyEye technique \valkyrie{can't add direct citation here??} (b) to sense the presence or absence of an object in each of its tubes.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:pens}
\end{figure}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{A neon sign designed using our tool.  The tubes contains four separate electroluminescent wires, lit in sequence to create animation (a).  (b) shows the selections we made to generate our tube structures.  (c) shows the internal structure of the tubes generated by our design tool.}
\label{fig:neon}
\end{figure}

>>>>

We created a touch-sensitive toy and an app that goes along with it, reminiscent of the boat application in \cite{Harrison-acoustic}.  This toy has an interior star topology where a single wire attached to an Arduino running an SFCS sketch splits to connect to sensors on the eyes, ears, tail, and nose.  To accompany this toy, we built an app which prompts the user to find and touch certain parts of the animal (see Figure \ref{fig:toy}).

\subsection{Braille Haptic Display}

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{When air pressure is changed in the six tubes, their caps inflate or deflate. Through controlled actuation, we can create Braille letters.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:braille}
\end{figure}

Using a $2\times3$ array of semi-closed tubes, we created a Braille output interface.  The closed ends of the tubes are covered in a rubberlike material, while on the system side the tubes are attached to individually-controlled air pumps.  These pumps can create positive or negative pressure in each tube, pushing the cap up or down and rendering a tactile Braille letter when used in concert (see Figure \ref{fig:braille}).

@@

A custom ``radio'' built using tubes allows users to tune to different stations and play sound files related to those stations.  This device uses a network of disconnected open tubes filled with conductive paint to connect traditional electronic components (a potentiometer, a piezo, and an LED) to a microcontroller.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This pen holder (a) uses the FlyEye technique (b) to sense the presence or absence of an object in each of its tubes.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:pens}
\end{figure}

Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:pens}).  Such information was used by \cite{Mueller-constructable} to determine which physical laser pointer a designer was using to interact with their interface.  Our pen holder uses the FlyEye technique described by Wimmer in \cite{Wimmer-flyeye} and contains open tubes filled with fiber optic cables, two per pen chamber.  One tube from each chamber leads to an infrared LED, and the other leads to a camera.  When a pen is in its appointed place, light from the LED is reflected off its bottom and travels through the other optical fiber into the camera, where it registers as a bright point.  A dark point on the camera region appears when a pen has been removed from its place, and the position of the point indicates which pen it is.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{A neon sign (a) and its partial duplicate designed using our tool (b).  (c) shows the selections we made to generate our tube structures.  (d) shows the internal structure of the tubes generated by our design tool.}
\label{fig:neon}
\end{figure}

Neon art, perhaps best known for its association with Las Vegas, is traditionally made from hand-formed glass tubes containing neon gas.  The tubes light up when a current is passed through them.  For this type of art, the path of the tubes is of crucial importance, as it determines how the sign will look.  We designed a partial duplicate of a renowned piece of neon art from Seattle (or was it Portland?).  The piece features open tubes due to support-flushing constraints, however the tubes could also be semi-closed.  They have been threaded with EL wire which is lit in sequence to create an animation.

### 2014-02-21 paper/limitations.tex
added more bib, fleshed out a few things, put some tables
more text, hooray

\section{Limitations}
Issues of drying time for fluids in long tubes.  Flexible material doesn't work forever.  Water in Objet prints discolors them.  Can be difficult to get certain materials through certain kinds of tubes.

>>>>

\section{Limitations and Future Work}
Tubes, while a powerful tool for directing interaction to arbitrary locations on an object's surface, have their shortcomings.  Most obviously, their fundamental shortfall is that they cannot replace the active elements required for a functioning interactive device: they simply redirect sensing to different locations on an object's surface.  All tubes need to, at some point, connect to a sensor, microcontroller, or pump.

Some media are difficult to insert in tubes, or may not be compatible with all types of tubes.  Fluids in particular provide challenges.  For example, the conductive paint we used in our designs can take multiple days to dry in tubes of sufficient length.  Any liquid kept in tubes printed by the Objet can cause the exterior of the part to discolor due to seepage.  Hobbyist machines do not guarantee watertightness of their prints, so leaking of water or air can occur.

The physical fabrication process also leads to some considerations.  To print without support on a hobbyist machine, internal tubes cannot have overhangs of greater than $45^{\circ}$.  On the Objet, support-free prints cannot overhang more than $14^{\circ}$.  Removal of support from printed tubes can be complicated, especially when their internal geometry and branching structures are complex.

Our design tool is not yet fully capable of realizing all possibilities in the design space of tubes.  It lacks X and Y \valkyrie{probably it will lack the network manipulation to make mixing or splitting tubes...?}.  We hope to address this in future work.

\valkyrie{what other future work?  miniaturization doesn't seem right, it's possible to use on mobile phones already with their on-board sensors (mic), maybe talking about shape-changing tubes?  post-fabrication modification with drills?  that doesn't sound very convincing.}

### 2014-02-21 paper/tubes.tex
more text, hooray

\subsubsection{Physical Simulation}

@@

@@

\subsubsection{printing} - different strategies with Objet (all print-in-place) and Makerbot (may need to add things like balloons afterwards).  Ryan just got flexible material, we should see how stretchy it is...!  We could also consider assembleable things that are easier to create using parts that clip together... probably out of scope.

\subsubsection{hand tools} - post-fabrication modification is possible using hand tools.  We can mark the surface to show where conduits are and how deep.  I can also use this to test things beforehand.

>>>>

Physical Simulation :

How does it actually work?

Bend Minimization

Collision detection

@@

How we actually cut stuff and make tubes happen.

@@

\subsubsection{Printing} - different strategies with Objet (all print-in-place) and Makerbot (may need to add things like balloons afterwards).  Ryan just got flexible material, we should see how stretchy it is...!  We could also consider assembleable things that are easier to create using parts that clip together... probably out of scope.

\subsubsection{Hand Tools} - post-fabrication modification is possible using hand tools.  We can mark the surface to show where conduits are and how deep.  I can also use this to test things before spending time printing them using a big ol' block o' plastic.
